---
title: "`drake` ~ live coding sesh ~"
author: "Amanda Dobbyn"
date: "February, 2019"
output: md_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(eval = FALSE)
knitr::opts_knit$set(eval = FALSE)
```

```{r}
# Will not be necessary to set in the upcoming release
pkgconfig::set_config("drake::strings_in_dots" = "literals")

# Grab all funs
source(here::here("R", "didnt_start_it.R"))
```


### Burner account time

Let's define a file path to dump the tweets we collect into.

```{r}
burner_path <- here("data", "raw", "burn.csv") # Same as "<working_dir>/data/raw/burn.csv"

# Delete the file in burner_path if it exists already so we start from scratch
if (file_exists(burner_path)) file_delete(burner_path)
```


Now we'll create our first draft of the plan:

```{r}
burner_plan <-
  drake_plan(
    # Reads in file from burner_path if file exists, otherwise pulls in seed tweets
    seed_burn = get_tweets(
      user = burner_handle,
      input_path = burner_path
    ),
    
    full_burn = get_tweets(
        tbl = seed_burn,
        user = burner_handle,
        output_path = burner_path # Outputs to burner_path
      )
  )
```

Every time `burner_plan` is run, new any tweets collected will be stored in `burner_path` and be read into the next iteration of `seed_burn`.

### Quick note on files

We're not using `drake`'s [`file_in`](https://ropensci.github.io/drake/reference/file_in.html) and [`file_out`](https://ropenscilabs.github.io/drake-manual/vis.html#output-files) functions, which allow `drake` to recognize and track the file. That lets us see when the targets associated with the file (both upstream and downstream of it) are invalidated.

### Test out v1 of our plan

Since `seed_burn` hasn't changed and the code to generate the targets hasn't changed, every time after the first time we run this plan `drake` will let us know that our targets are up to date and not re-run anything.

```{r}
# Take a look at the dataframe that represents our plan
burner_plan 

# Save the config in an object we can look at
burner_config <- drake_config(burner_plan)

# Remove targets if they were already built
clean() 

# Both seed_burn and full_burn should be outdated
vis_drake_graph(burner_config)

# Make the plan
make(burner_plan, verbose = 4)

# Everything should already be up to date 
outdated(burner_config)

# Which is reflected in our graph
vis_drake_graph(burner_config)

# Can show just targets if things are too crowded
vis_drake_graph(burner_config, targets_only = TRUE)
```

We can now load these targets into our working environment.

```{r}
# They won't be found if we don't loadd() them
seed_burn

loadd(seed_burn)
seed_burn
```


Every subsequent time we re-`make` the plan, `drake` should tell us we don't need to do anything.

```{r}
# Unloads (removes) the global variable seed burn we've loadd'd to prevent conflicts
make(burner_plan)
# Not in our env anymore
seed_burn

make(burner_plan)
make(burner_plan)
```

If we `clean()`, however, we'll remake the plan from scratch.

```{r}
clean()

# Targets we built are gone from the cache
loadd(seed_burn)

# Targets are outdated now
vis_drake_graph(burner_config, targets_only = TRUE) 

# Make the plan again.
# Since we saved the previous output of full_burn to a file, this time we read that in for our seed_burn
make(burner_plan) 

# And now everything is up to date again
vis_drake_graph(burner_config, targets_only = TRUE) 
```


### Changing Code

One way we can guarantee that `drake` will re-`make` a target is if some part of the code used to generate that target changes.

Right now, nothing outdated becuase we just ran `make(burner_plan)`.

```{r}
outdated(burner_config)
```

Let's modify the code to a function called by `get_tweets`. Note that `drake` recognizes that targets that incorporate this function at some point in the pipeline are out of date, even though this function isn't called in the plan directly.

Our original function, `there_are_new_tweets` which checks if the specified user has tweeted anything since the most recent tweet in our `tbl` argument:

```{r}
there_are_new_tweets <- function(tbl,
                                 user = firewire_handle,
                                 verbose = TRUE) {
  latest_dt <-
    tbl %>%
    arrange(desc(created_at)) %>%
    slice(1) %>%
    pull(created_at)

  if (verbose) message("Searching for new tweets.")

  new <- get_seed_tweets(user = user, n_tweets = 1)

  if (max(new$created_at) <= latest_dt) {
    if (verbose) message("No new tweets to pull.")
    FALSE
  } else {
    TRUE
  }
}
```


We'll change the message to include a smiley emoji `emo::ji('smile')` when `there_are_new_tweets` is called.

```{r}
there_are_new_tweets <- function(tbl,
                                 user = firewire_handle,
                                 verbose = TRUE) {
  latest_dt <-
    tbl %>%
    arrange(desc(created_at)) %>%
    slice(1) %>%
    pull(created_at)

  if (verbose) message(glue("Searching for new tweets! {emo::ji('smile')}"))

  new <- get_seed_tweets(user = user, n_tweets = 1)

  if (max(new$created_at) <= latest_dt) {
    if (verbose) message("No new tweets to pull.")
    FALSE
  } else {
    TRUE
  }
}
```


Without doing anything else, we can check that both targets which had been up to date has now been invalidated. 

```{r}
outdated(burner_config)
vis_drake_graph(burner_config)
```

Notice that we didn't even need to re-define our plan; `drake` can tell that a function a target in our plan relies on has meaningfully changed.

When we re-`make` our plan we should be messaged an `r emo::ji("smile")`.

```{r}
make(burner_plan)
```

And now `seed_burn` and `full_burn` should both be up to date again.

```{r}
outdated(burner_config)
vis_drake_graph(burner_config)
```



### Add Triggers

I mentioned that a way to guarantee that targets are re-made even if code *doesn't* change is to associate a trigger with a target.

Let's add a [trigger](https://ropensci.github.io/drake/articles/debug.html#test-with-triggers-) so that we always run `get_tweets` to look for new tweets at the burner handle.


```{r}
burner_plan_2 <-
  drake_plan(
    seed_burn = get_tweets(
      user = burner_handle,
      input_path = burner_path
    ),
    
    full_burn = target(
      command = get_tweets(
        tbl = seed_burn,
        user = burner_handle,
        output_path = burner_path 
      ),
      trigger = trigger(
        condition = TRUE
      )
    )
  )
```


This trigger will make our `full_burn` target look always out of date to `drake` since it knows we need to re-make `full_burn` every time `make()` is run.

Our `condition` always evaluates to `TRUE` because it's just the value `TRUE`, but you can also sub in any expression that returns a boolean.

```{r}
is_even_day <- function(input_date = Sys.Date()) {
  this_day <- 
    input_date %>% lubridate::day()
  
  this_day %% 2 == 0
}

is_even_day()
is_even_day(Sys.Date() + 1)
is_even_day(Sys.Date() + 2)
```


### Test out the `burner_plan` 2.0

First we'll clean out the previous file we saved and start from scratch.

```{r}
if (file_exists(burner_path)) file_delete(burner_path)
```


Our `full_burn` target will always be out of date because the trigger indicates that it always needs to be rebuilt, but `seed_burn` will now be up-to-date.

```{r, eval=FALSE}
clean()

# Notice our new trigger column
burner_plan_2 

# seed_burn is outdated becuase we haven't made the plan yet.
# full_burn is always out of date, no matter what, because of the trigger.
burner_config_2 <- drake_config(burner_plan_2)
outdated(burner_config_2)
vis_drake_graph(burner_config_2)
```

All tweets are now stored in `burner_path`, which we specified as our `output_path` when making `full_burn`.

What's stored in this file is the same as both `seed_burn` and `full_burn` becuase there were no tweets posted between when we made `seed_burn` and `full_burn`.

```{r}
make(burner_plan_2)

# Load the results of seed_burn and full_burn into our environment
loadd(seed_burn)
loadd(full_burn)
# These should be the same since no new tweets posted
expect_identical(seed_burn, full_burn)

# full_burn always outdated, seed_burn no longer outdated
outdated(burner_config_2)
vis_drake_graph(burner_config_2, targets_only = TRUE)
```


Now let's post a new tweet and re-`make` the plan.

`seed_burn` will be read in from the file, which reflects the state of the world before this tweet. Then `full_burn` will incorporate the new tweet.

```{r}
# Tweet here
post_tweet(status = 
             digest::digest(sample(100, 1)), 
           token = firewire_token)


# seed_burn (read from file) is up to date, and full_burn will always look outdated
make(burner_plan_2)
vis_drake_graph(burner_config_2, targets_only = TRUE) 

loadd(seed_burn)
loadd(full_burn)
# We should have one extra row in full_burn than in seed_burn, because seed_burn wasn't rebuilt
expect_gt(nrow(full_burn), nrow(seed_burn)) 

seed_burn
full_burn

# Let's check that full_burn was saved to file
saved_burn <- read_csv(burner_path)
expect_identical(nrow(full_burn), nrow(saved_burn))
```

Now we've proven that we can successfully trigger the re-building of `full_burn` every time and save it as the latest state of the world to a file. 

Every time new tweets arrive, that file will be updated at the end of the `make()` run.


### Write our full plan

Let's go back to our original NYCFireWire Twitter account.

For the purposes of illustration, I'll set a `max_id` on our `seed_fires` so that we can re-up and grab more tweets to build `fires`.

```{r}
fire_path <- here("data", "raw", "fires.csv")
if (file_exists(fire_path)) file_delete(fire_path)
```

```{r}
plan <-
  drake_plan(
    seed_fires = get_tweets( 
      n_tweets_seed = 2,
      max_id = old_tweet_id,
      input_path = fire_path
    ), 
    fires = target(
      command = get_tweets(
        tbl = seed_fires,
        n_tweets_reup = 3,
        output_path = fire_path
      ),
      trigger = trigger(
        condition = TRUE # Always look for new tweets
      )
    ),
    addresses = pull_addresses(fires), # Extract addresses from tweets
    lat_long = get_lat_long(addresses), # Send to Google for lat-longs
    fire_sums = count_fires(lat_long), # Sum up n fires per lat-long combo

    time_graph = graph_fire_times(lat_long),
    plot = plot_fire_sums(fire_sums)
  )
```

### Run our plan

```{r}
plan

make(plan, verbose = 4)

# See what a couple of our targets look like
loadd(addresses)
addresses

loadd(lat_long)
lat_long

loadd(time_graph)
time_graph
```

### Info drake stores

Let's get a little deeper into what `drake` stores in the `config`.

```{r, eval=FALSE}
config <- drake_config(plan)
sort(names(config))
config$plan
config$targets
config$cache_path
config$graph

# The dependencies of a given target encompass both functions (get_tweets) and targets that it depends on (seed_fires)
deps_target(addresses)

# You can get even more granular with
dependency_profile(addresses, config)

# Since we have a trigger on fires, everything downstream of fires is also perpetually outdated
outdated(config)
vis_drake_graph(config)

# We can clean just one target instead of cleaning everything
clean(fires)

# Since we didn't clean() seed_fires (upstream of fires), this target remains built and our dependency graph looks the same
vis_drake_graph(config)

# And again, if we re-make the plan we'll pull in new tweets because of our trigger
make(plan)
```

### Previously `geocode`d

For kicks, let's make our plots with data from 3000 tweets pulled from NYCFireWire and sent to Google for geocoding. 

We'll stop at `pull_addresses(fires)` so we don't re-geocode all 3k fires.

We'll set the `input_path` to `seed_fires` to that file, and still grab the most recent 3 tweets.

```{r}
big_plan <-
  drake_plan(
    seed_fires = get_tweets( # Grab seed fires from file
      input_path = here("data", "raw", "lots_o_fires.csv")
    ), 
    fires = target(
      command = get_tweets(
        tbl = seed_fires,
        n_tweets_reup = 3
      ),
      trigger = trigger(
        condition = TRUE 
      )
    ),
    addresses = pull_addresses(fires)
    # Not sending all 3k addresses to Google
  )

make(big_plan)

loadd(addresses)
nrow(addresses)
addresses
```

Make our quick plot from the 3k fires:

```{r}
lat_long <- 
  read_csv(here("data", "derived", "lat_long.csv"))

fire_sums <-
  read_csv(here("data", "derived", "fire_sums.csv"))

graph_fire_times(lat_long)
plot_fire_sums(fire_sums)
```


### That's all!

Any q's?


