---
title: "pres"
author: "Amanda Dobbyn"
date: "1/20/2019"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source(here::here("didnt_start_it.R"))
```

### Quick about me

### `drake`'s main idea

In a pipeline, when changes occur that make the most recent results out-of-date, rebuild *only* the parts of the pipeline that need to be rebuilt.

### What is `drake`?

[GNU Make](https://www.gnu.org/software/make/) for R, built around dataframes.

GNU Make uses a file called a Makefile to specify dependencies and how targets should be reubilt when they're out of date. 

Created and maintained by [Will](https://twitter.com/wmlandau) [Landau](https://github.com/wlandau) and friends.

### Two pieces of vocab

*targets* and *commands*
From `?drake_config`: "**Targets** are the objects and files that drake generates, and **commands** are the pieces of R code that produce them."

### Other nice features of `drake`
1. See how your pipeline fits together, in a tidy dataframe
2. Visualize dependencies in your code in graph format
3. Some high-performance computing advantages
4. Great for reproducibility
5. It's all in R!

### How to `drake`:
1. Store prework (loading packages and user-defined functions) in a file
2. Store a `drake` plan in another file
3. Create the plan and run it

```{r, eval=FALSE}
source("/path/to/my/prework.R")

# Custom functions defined in prework are:
# clean_my(), analyze_my(), and report_out_my()

plan <- 
  drake_plan(
  cleaned_data = clean_my(raw_data),
  results = analyze_my(cleaned_data),
  report = report_out_my(results,
                         file_out = "/path/to/my/report.md")
)

make(plan)
```

The first run of `make(plan)` will run the plan from scratch. 

After that, `drake` will only re-run the parts of the plan that are out of date, and all those parts' dependencies.


### What makes a target become out of date?

1. Some part of the code used to generate that target or one of its upstream targets has changed
2. A trigger is activated (more on that later)

### Where is all this stored?

How does `drake` store info/data about targets?
In a hidden `.drake` directory. In the `.drake/data` subdirectory, targets are stored as `rds` objects.

How does `drake` keep track of dependencies?
With a `config` which you can access.

### Big Idea #2

`drake` is all built around *functions* rather than sourcing scripts.
- A plan works by using functions to create targets. 
- Running `drake_plan` creates a dataframe relating each target to the function used to generate it.


```{r, eval=FALSE}

bad_plan <- 
  drake_plan(
    first_target = source("import.R"),
    second_target = source("clean.R")
  )
```


Instead, 

```{r, eval=FALSE}

source("all_my_funs.R")

good_plan <- 
  drake_plan(
    first_target = do_stuff(dat),
    second_target = do_more_stuff(first_target)
  )
```


### Our plan

Remember the [crazy blue light](https://twitter.com/NYCFireWire/status/1078478369036165121) from late December?

The Twitter account that let us know that this wasn't in fact aliens is [NYCFireWire](https://twitter.com/NYCFireWire).

Normally they just tweet out fires and their locations in a more or less predictable pattern, e.g.

https://twitter.com/NYCFireWire/status/1087888350277705728


What if we were constructing an analysis of these tweets and wanted to make sure our pipeline worked end-to-end, but didn't want to unnecessarily re-run outdated parts of it unless we needed to?


### The Pipeline

1. Pull in tweets, either the first big batch or any new ones that show up
2. Extract addresses from the tweets (`r emo::ji("notes")` regex time `r emo::ji("notes")`)
3. Send these to the Google Maps API to grab the addresses' latitudes and longitudes
4. Profit


### Grabbing tweets

- `get_seed_tweets` grabs a batch of tweets *or* reads in seed tweets from a file if the file exists
- `get_more_tweets` checks if there are new tweets and, if so, pulls in the right number of them
- `get_tweets` runs `get_seed_tweets` if given a null `tbl` argument, otherwise runs `get_more_tweets`

```{r, include=FALSE}
get_seed_tweets

get_more_tweets

get_tweets
```

```{r}
get_tweets()

old_tweet_id <- "1084619203167031297" # Random tweet from a while ago

get_tweets(
  max_id = old_tweet_id
  ) %>% 
  get_tweets(n_tweets_reup = 5)
```


### Getting addresses

```{r, include=FALSE}
borough_reg

clean_borough

pull_addresses
```

```{r}
get_tweets() %>% 
  pull_addresses() %>% 
  select(street, borough, address, text)
```


Then we can use the `geocode` function (along with a Google Maps API key) from the `ggmap` package to attach the latitude and longitude to each address, if Google can find it.

```{r}
geo_to_list

truncate_lat_long

get_lat_long
```

```{r}
get_tweets(n_tweets_seed = 5) %>% 
  pull_addresses() %>% 
  get_lat_long()
```


### Write our plan

```{r}
fire_path <- here("data", "raw", "fires.csv")

plan <-
  drake_plan(
    seed_fires = get_tweets( # Grab some seed fires
      n_tweets_seed = 2,
      max_id = old_tweet_id
    ), 
    fires = target(
      command = get_tweets(
        tbl = seed_fires,
        n_tweets_reup = 3
      ),
      trigger = trigger(
        condition = TRUE # Always look for new tweets
      )
    ),
    addresses = pull_addresses(fires), # Extract addresses from tweets
    lat_long = get_lat_long(addresses), # Send to Google for lat-longs
    dat = join_on_city_data(lat_long, nyc), # Join on the nyc coords
    fire_sums = count_fires(dat), # Sum up n fires per lat-long combo

    time_graph = graph_fire_times(dat),
    plot = plot_fires(dat, nyc)
  )
```

### Run our plan

```{r}
plan

make(plan, verbose = 4)
```

### Info drake stores

```{r, eval=FALSE}
config <- drake_config(plan)
config$plan
config$prework
config$targets
config$cache_path
config$graph

vis_drake_graph()

lat_long
loadd(lat_long)
lat_long

clean(fires)

outdated(config)

vis_drake_graph()

make(plan)

loadd(lat_long)
lat_long
```

If our `seed_fires` had been 3000 instead of 3:

```{r}
big_plan <-
  drake_plan(
    seed_fires = get_tweets( # Grab seed fires from file
      input_path = here("data", "derived", "lots_o_fires.csv")
    ), 
    fires = target(
      command = get_tweets(
        tbl = seed_fires,
        n_tweets_reup = 3
      ),
      trigger = trigger(
        condition = TRUE 
      )
    ),
    addresses = pull_addresses(fires)
    # Not sending all 3k addresses to Google
  )

make(big_plan)

loadd(addresses)
addresses

make(big_plan)
```


### Testing our reupping with a `r emo::ji("fire")` burner account `r emo::ji("fire")`

The `rtweet` package also supports posting tweets, so we can test out whether our trigger successfully pulls in new tweet by posting ourselves.

[Burner account!](https://twitter.com/didntstartit)

Every time `burner_plan` is run, new any tweets collected will be stored in `burner_path` and be read into the next iteration of `seed_burn`.

Let's pre-store all tweets in burner_path.

```{r}
burner_path <- "data/derived/burn.csv"

get_tweets(
      user = burner_handle,
      output_path = burner_path
    )

read_csv(burner_path)
```


Now we'll create the plan:

```{r}
burner_plan <-
  drake_plan(
    # Reads in file from burner_path if file exists, otherwise pulls in seed tweets
    seed_burn = get_tweets(
      user = burner_handle,
      input_path = burner_path 
    ),
    
    full_burn = target(
      command = get_tweets(
        tbl = seed_burn,
        user = burner_handle,
        output_path = burner_path # Outputs to burner_path
      ),
      trigger = trigger(
        condition = TRUE # Always look for new tweets
      )
    )
  )

burner_plan
```

### Test out the burner

The data in `burner_path` should be all the tweets this burner account has tweeted so far:

```{r, eval=FALSE}
burner_config <- drake_config(burner_plan)
vis_drake_graph(burner_config)

make(burner_plan)
loadd(seed_burn)
loadd(full_burn)
expect_equal(seed_burn, full_burn)
```

Now let's post a new tweet.

```{r}
outdated(burner_config)

# Tweet here
post_tweet(status = 
             digest::digest(sample(100, 1)), 
           token = firewire_token)

make(burner_plan)

loadd(seed_burn)
loadd(full_burn)

# And let's checked it was saved to file
saved_burn <- read_csv(here("data", "derived", "burn.csv"))
expect_gt(nrow(full_burn), nrow(seed_burn))
expect_equal(nrow(full_burn), nrow(saved_burn))

clean()

outdated(burner_config)

make(burner_plan)
loadd(seed_burn)
loadd(full_burn)
expect_equal(nrow(seed_burn), nrow(full_burn))
```


### Moar Resources
[`drake` user manual`](https://ropenscilabs.github.io/drake-manual/index.html)
[Kirill Müller's cheat sheet](https://github.com/krlmlr/drake-sib-zurich/blob/master/cheat-sheet.pdf)
